---
title: "Unit 12 Q3.3"
author: "Duy Vo (duyvo@berkeley.edu)"
format: pdf
---

```{r setup, echo=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(readr)
library(tidyverse)

source("analysis.R")
```

```{r plot_lm_model}
#| echo: false
#| fig-cap: "Residuals vs Fitted Values Plot of Linear Model"
#| fig-pos: H
#| label: fig-plot_lm_model

plot(lm_model, which = 1)
```

By visually inspecting @fig-plot_lm_model, we can see that the residuals are mostly not scattered around a horizontal line at 0, therefore the data is likely not linear.

```{r plot_dreaming}
#| echo: false
#| fig-cap: "dreaming vs brain_wt"
#| fig-pos: H
#| label: fig-plot_dreaming
#| message: false
#| warning: false

ggplot(mammals_data, aes(x = brain_wt, y = dreaming)) +
  geom_point() +
  geom_smooth(method = "loess", color = "blue")
```

```{r plot_non_dreaming}
#| echo: false
#| fig-cap: "non_dreaming vs brain_wt"
#| fig-pos: H
#| label: fig-plot_non_dreaming
#| message: false
#| warning: false

ggplot(mammals_data, aes(x = brain_wt, y = non_dreaming)) +
  geom_point() +
  geom_smooth(method = "loess", color = "blue")
```

We can verify the non-linearity of the data by looking at @fig-plot_dreaming and @fig-plot_non_dreaming and confirm that the plots aren't linear. Finally, \ref{eq:lm_model} has an adjusted $R^2$=`r lm_model_summary$adj.r.squared` whereas \ref{eq:lm_model} has a higher adjusted $R^2$=`r inverse_lm_model_summary$adj.r.squared`.

\begin{equation}
{brain_wt} = \beta_0 + \beta_1{dreaming} + \beta_2{non\_dreaming} \label{eq:lm_model}
\end{equation}

\begin{equation}
{brain_wt} = \beta_0 + \beta_1{dreaming} + \beta_2{non\_dreaming} + \beta_3{dreaming}^2 + \beta_4{non\_dreaming}^2 \label{eq:inverse_lm_model}
\end{equation}