---
title: "Q3.2"
author: "Duy Vo (duyvo@berkeley.edu)"
format: pdf
---

```{r setup, echo=FALSE, message=FALSE}
library(broom)
library(dplyr)
library(ggplot2)
library(lubridate)
library(readr)

current_date <- Sys.Date()

legislators_data <- read_csv("data/legislators-current.csv")
senators_data <- legislators_data %>%
  select(`birthday`, `party`) %>%
  mutate(
    age_years = time_length(interval(as.Date(birthday), current_date), unit = "year")
  ) %>%
  filter(`party` %in% c("Democrat", "Republican"))

```

In order to use the Wilcoxon Rank-Sum test, we make the assumptions:

1. The data must be independent and identically-distributed. We assume that the data iid because we have the full population and we assume that the election of one senator does not impact the election of another senator
1. Since we are comparing age, we need the age to be at least of an ordinal scale in the hierarchy of data. Since age is often considered a ratio level, we have met this requirement because ratio level is higher than ordinal level.

```{r plot_data}
#| echo: false
#| fig-cap: "Median age of senators by major party"
#| fig-pos: H
#| label: fig-plot

ggplot(
  data = senators_data,
  aes(x = `party`, y = `age_years`, fill = `party`)
  ) +
  geom_boxplot() +
  scale_fill_manual(values = c(`Democrat` = "blue", `Republican` = "red")) +
  labs(
    x = "Major Party",
    y = "Age (Years)",
    fill = "party"
  )


```

```{r analysis, echo=FALSE}
test_result <- wilcox.test(age_years ~ party, data = senators_data)
tidy_result <- tidy(test_result)

democrat_count <- sum(senators_data$party == 'Democrat')
republican_count <- sum(senators_data$party == 'Republican')
total_number_of_entries <- democrat_count + republican_count

s_observed <- tidy_result$statistic + ((democrat_count * (democrat_count + 1))/2)
s_expected <- (democrat_count * (total_number_of_entries + 1)) / 2
```

Visually, from @fig-plot, it's not clear that there is a significant difference. However, with a $p-value$ of `r tidy_result$p.value`, we can say that our findings is statistically significant. Examining the Democratic Senators, with $S_{observed}=$`r s_observed` $>$ $S_{expected}=$ `r s_expected`, we can say that the median age of Democratic Senators is higher than those of Republican Senators, which is consistent with @fig-plot.