---
title: "Q3.3"
author: "Duy Vo (duyvo@berkeley.edu)"
format: pdf
---

In order to run a Wilcoxon Signed-Rank Test, we make the following assumptions:

1. There is a relationship between heart disease and liver disease for a given country. Given that the values are per-country, this condition is met.
1. The data must be independent and identically-distributed. We assume that the data iid because it's collected for different countries and we don't have strong enough evidence to think that countries will impact each other.
1. The data must be continuous. Since this is a count, we can assume the data is likely countably continuous.
1. The data can't be too skewed. Looking at @fig-data_diff_plot (red is mean, blue is median), we have no evidence the data is skewed.

```{r setup, echo=FALSE}
library(ggplot2)
library(broom)
library(wooldridge)

# data(package = "wooldridge")
data("wine")

wine$diff <- wine$heart - wine$liver

# ?wine
# head(wine)
```

```{r draw_plot}
#| label: fig-data_diff_plot
#| fig-cap: "Difference between heart and liver disease death per 100,000 per country"
#| fig-pos: H
#| echo: false
#| warning: false

ggplot(wine,
       aes(x = diff)) +
  geom_histogram(bins = 10) +
  geom_vline(aes(xintercept = mean(diff)), color = "red", linetype = "dashed", size = 1) +
  geom_vline(aes(xintercept = median(diff)), color = "blue", linetype = "dashed", size = 1) +
  labs(title = "Histogram of Differences (Heart - Liver)",
       x = "Difference in Death Rates",
       y = "Frequency")
```

```{r analysis, echo=FALSE}
# summary(wine$diff)
test_result <- wilcox.test(wine$heart, wine$liver, paired = TRUE)
tidy_result <- tidy(test_result)
# print(tidy_result)
```

The dataset has 21 entries, giving us an $S_{expected} = \frac{n(n+1)}{4} = \frac{21*22}{4} = 115.5$. Since the statistic of `r tidy_result$statistic` is much greater than $S_{expected}$, we can confidently say that the number of deaths associated with heart disease is greater than liver disease. With a $p-value$ of `r tidy_result$p.value`, we can say that our findings is statistically significant.