---
title: "Q3.3"
author: "Duy Vo (duyvo@berkeley.edu)"
format: pdf
---

In order to run a Wilcoxon Signed-Rank Test, we make the following assumptions:

1. There is a relationship between heart disease and liver disease for a given country. Given that the values are per-country, this condition is met.
1. The data must be independent and identically-distributed. We assume that the data iid because it's collected for different countries and we don't have strong enough evidence to think that countries will impact each other.
1. The data must be continuous. Since this is a count, we can assume the data is likely countably continuous.
1. The data can't be too skewed. Looking at @fig-data_diff_plot (red is mean, blue is median), we have no evidence the data is skewed.

```{r setup, echo=FALSE, message=FALSE}
library(ggplot2)
library(broom)
library(wooldridge)

# data(package = "wooldridge")
data("wine")

wine$diff <- wine$heart - wine$liver

# ?wine
# head(wine)
```

```{r draw_plot_diff}
#| label: fig-data_diff_plot
#| fig-cap: "Difference between heart and liver disease death per 100,000 per country"
#| fig-pos: H
#| echo: false
#| warning: false

ggplot(wine,
       aes(x = diff)) +
  geom_histogram(bins = 10) +
  geom_vline(aes(xintercept = mean(diff)), color = "red", linetype = "dashed", size = 1) +
  geom_vline(aes(xintercept = median(diff)), color = "blue", linetype = "dashed", size = 1) +
  labs(title = "Histogram of differeces (Heart - Liver)",
       x = "Difference in Death Rates",
       y = "Frequency")
```

```{r plot_data}
#| echo: false
#| fig-cap: "Deaths by heart and liver -related disease per 100,000"
#| fig-pos: H
#| label: fig-plot_data

ggplot(data = wine) +
  geom_segment(aes(y = wine$country, yend = wine$country, x = wine$heart, xend = wine$liver), color = "gray80", size = 1) +
  geom_point(aes(y = wine$country, x = wine$heart, color = "Heart Disease"), size = 3) +
  geom_point(aes(y = wine$country, x = wine$liver, color = "Liver Disease"), size = 3) +
  scale_color_manual(name = "Cause of Death", 
                     values = c("Heart Disease" = "red", "Liver Disease" = "blue")) +
  labs(
    x = "Number of Deaths",
    y = NULL
  )


```

```{r analysis, echo=FALSE}
# summary(wine$diff)
test_result <- wilcox.test(wine$heart, wine$liver, paired = TRUE)
tidy_result <- tidy(test_result)
# print(tidy_result)
```

With a $p-value$ of `r tidy_result$p.value`, we can say that our findings is statistically significant. $W=$ `r tidy_result$statistic` tells us that the deaths from heart disease is higher than liver disease, which we can visually confirm with @fig-plot_data.