---
title: "Q3.4"
author: "Duy Vo (duyvo@berkeley.edu)"
format: pdf
---

```{r setup, echo=FALSE, message=FALSE}
library(broom)
library(dplyr)
library(ggplot2)
library(readr)

religion_data <- read_csv("data/GSS_religion.csv")
number_of_entries <- nrow(religion_data)
```

I am implementing a two-sample t-test to determine whether people in the US feel more positive towards Catholics or Protestants. a t-test requires the following conditions:

1. Since we have `r number_of_entries` observations, which is greater than 30, we can rely on the CLT for a normally-distributed sampling distribution of the sample mean. This meets the normal distribution requirement for the t-test.
1. The data must be independent and identically-distributed. We assume that the author of the collected data selected individuals for the study in a way that the respondents are iid.
1. We are only comparing two groups (Catholics and Protestants).

```{r plot_data}
#| echo: false
#| fig-cap: "Warmness felt by US respondents towards Catholics and Protestants"
#| fig-pos: H
#| label: fig-plot_data

religion_with_frequency_df <- religion_data %>%
  count(cathtemp, prottemp, name = "Frequency")

ggplot(data = religion_with_frequency_df,
       aes(x = cathtemp, y=prottemp)) +
  geom_point(aes(size = Frequency), alpha = 0.6, color = "blue") +
  scale_size_continuous(range = c(1, 10)) +
  labs(
    x = "Warmness towards Catholics",
    y = "Warmness towards Protestants"
  ) +
  guides(size = "none")
```

```{r analysis, echo=FALSE}
test_result <- t.test(
  religion_data$cathtemp,
  religion_data$prottemp,
  paired=TRUE
)
# print(test_result)
tidy_result <- tidy(test_result)

mean_cathtemp <- mean(religion_data$cathtemp)
mean_prottemp <- mean(religion_data$prottemp)
mean_precent_difference <- abs(mean_cathtemp - mean_prottemp) / ((mean_cathtemp + mean_prottemp) / 2) * 100
```

From @fig-plot_data, it's not clear that there is a significant difference between the warmness respondents feel towards Catholics or Protestants. However, the t-test produced a $p-value$ of `r tidy_result$p.value`, so we believe that there is a difference. A t-statistic of `r tidy_result$statistic` tells us that respondents are warmer towards Protestants than Catholics. By examining the mean the respondents' warmness towards Catholics ($\bar{x}=$ `r mean_cathtemp`) and Protestants ($\bar{x}=$ `r mean_prottemp`) representing a perecent difference of `r mean_precent_difference`%, we believe that there isn't a significantly more warmness towards Protestants than Catholics.